### 2015-06-05 chapters/ipa_meets_unicode.tex
reverting this morning's width adjustments

\begin{itemize}
	\item Basic Latin (30 characters), e.g. <a, b, c, d, e> \item Latin-1
	Supplement (4 characters): <æ, ç, ð, ø\textgreater{} \item Latin
	Extended-A (3 characters): <ħ, ŋ, œ> \item Latin Extended-B (5
	characters): <ǀ, ǁ, ǂ, ǃ, > \item IPA Extensions (70 characters), e.g.:
	<ɐ, ɑ, ɔ> \item Spacing Modifier Letters (20 characters), e.g.: <ʰ ʷ ˥>
	\item Combining Diacritical Marks (33 characters), e.g.: <̝ ̥ ̪> \item
	Greek and Coptic (3 characters): <β, θ, χ> \item Phonetic Extensions (2
	characters): <, > \item Phonetic Extensions Supplement (3 characters): <
	, , > \item Superscripts and Subscripts (1 character): <ⁿ> \item Arrows
	(2 characters): \textless{}↑, ↓\textgreater{} \item Latin Extended-C (1
	character): <>
\end{itemize}

>>>>

\begin{itemize}
	\item Basic Latin (30 characters), e.g. <a, b, c, d, e> 
	\item Latin-1 Supplement (4 characters): <æ, ç, ð, ø\textgreater{} 
	\item Latin Extended-A (3 characters): <ħ, ŋ, œ> 
	\item Latin Extended-B (5 characters): <ǀ, ǁ, ǂ, ǃ, ȵ> 
	\item IPA Extensions (70 characters), e.g.: <ɐ, ɑ, ɔ> 
	\item Spacing Modifier Letters (20 characters), e.g.: <ʰ ʷ ˥> 
	\item Combining Diacritical Marks (33 characters), e.g.: <̝ ̥ ̪> 
	\item Greek and Coptic (3 characters): <β, θ, χ> 
	\item Phonetic Extensions (2 characters): <ᴅ, ᴴ> 
	\item Phonetic Extensions Supplement (3 characters): <ᶑ , ᶾ, ᶣ> 
	\item Superscripts and Subscripts (1 character): <ⁿ> 
	\item Arrows (2 characters): \textless{}↑, ↓\textgreater{} 
	\item Latin Extended-C (1 character): <ⱱ> 
\end{itemize}

### 2015-06-05 chapters/pitfalls.tex
reverting this morning's width adjustments

The problem with blocks arises because finding the right character among the
thousands of Unicode characters is not easy. Many software applications present
blocks as a primary search mechanism, because the block names suggest where to
look for a particular character. However, when a user searches for an IPA
character in the block \textsc{IPA Extensions} then many IPA characters will not
be found there. For example, the velar nasal <Å> is not part of the block
\textsc{IPA Extensions} because it was already included as LATIN SMALL LETTER
ENG at U+014B in the block \textsc{Latin Extensions-A}.

@@

First, \textit{a single character may have different contextually determined
glyphs.} For example, characters in writing systems like Hebrew and Arabic have
different glyphs depending on where they appear in a word. Some letters in
Hebrew change their form at the end of the word, and in Arabic, primary letters
have four contextually-sensitive variants (isolated, word initial, medial and
final). Second, \textit{a single character may be rendered as a sequence of
multiple glyphs.} For example, in Tamil one Unicode character may result in a
combination of a consonant and vowel, which are rendered as two adjacent glyphs
by fonts that supports Tamil. Third, \textit{a single glyph may be a combination
of multiple characters.} For example, the ligature <ï¬>, a single glyph, is the
result of two characters, <f> and <i>, that have undergone glyph substitution by
font rendering. Like contextually-determined glyphs, ligatures are (intended)
artifacts of text processing instructions. Finally, \textit{a single glyph may
be a part of a character} (e.g.~diacritics).

>>>>

The problem with blocks arises because finding the right character among the thousands of Unicode characters is not easy. Many software applications present blocks as a primary search mechanism, because the block names suggest where to look for a particular character. However, when a user searches for an IPA character in the block \textsc{IPA Extensions} then many IPA characters will not be found there. For example, the velar nasal <Å> is not part of the block \textsc{IPA Extensions} because it was already included as LATIN SMALL LETTER ENG at U+014B in the block \textsc{Latin Extensions-A}.

@@

First, \textit{a single character may have different contextually determined glyphs.} For example, characters in writing systems like Hebrew and Arabic have different glyphs depending on where they appear in a word. Some letters in Hebrew change their form at the end of the word, and in Arabic, primary letters have four contextually-sensitive variants (isolated, word initial, medial and final). Second, \textit{a single character may be rendered as a sequence of multiple glyphs.} For example, in Tamil one Unicode character may result in a combination of a consonant and vowel, which are rendered as two adjacent glyphs by fonts that supports Tamil. Third, \textit{a single glyph may be a combination of multiple characters.} For example, the ligature <ï¬>, a single glyph, is the result of two characters, <f> and <i>, that have undergone glyph substitution by font rendering. Like contextually-determined glyphs, ligatures are (intended) artifacts of text processing instructions. Finally, \textit{a single glyph may be a part of a character} (e.g.~diacritics).
